%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Karine Pires based on Andy Freeland code, available at https://github.com/rouge8/resume .
% resume class by Michael DeCorte
\documentclass[margin,centered,10pt]{resume}
\usepackage[utf8x]{inputenc}
\usepackage[x11names]{xcolor}
\usepackage{calc}
\definecolor{resumecolor}{HTML}{26938A}
% \newsectionwidth{2.5cm}
% \newresumewidth{10cm}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\huge Karine Pires} 
\address{\small6 Rue Madeleine Brès, Apt 409, 75013, Paris 
\textcolor{resumecolor}{$\bullet$} +33 7 87 16 72 62 
\textcolor{resumecolor}{$\bullet$} pires.karine@gmail.com 
\textcolor{resumecolor}{$\bullet$} https://github.com/karinepires}
\hyphenpenalty=1000 %sets the penalty for hyphenation so high that it will never happen.
\begin{resume}
    \vspace{-2.8mm}
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textcolor{resumecolor}{Education}}

    \textbf{Université Pierre et Marie Curie}, Paris, France.
    \hfill 2012 – present\\
    \textbf{Telecom Bretagne}, Rennes, France.    
    \\
    \textsl{Ph.D. in Computer Science.}
    \vspace{-3mm}\\\vspace{-1mm}%
    \begin{list3}
        \item Thesis title: Delivery, Transcoding and Neutrality on Large Live Streaming Systems. Advisors: Dr. Sébastien Monnet and Dr. Gwendal Simon. % Associated teams: Regal research group of LIP6/INRIA at UPMC and Networks, Security, Multimedia Department at Telecom Bretagne.
        %\item Orchestration of multiple machines and creation of tools to continuously interact with justin.tv and YouTube Live APIs. Expertise on programing languages and manipulation of SQLite sharded databases in order to extract analytical information from APIs data.
        \item Orchestration of multiple machines and creation of tools (PHP, Python and R) to interact with Twitch and YouTube APIs, in order to retrieve live streaming systems snapshots.
        \item Development with CPLEX IBM (on Python and C++) to solve ILP of hybrid live stream delivery.
        %\item Collaborations with multiple projects and teams. %Usage of multiple version control/sharing tools (GIT, SVN, DropBox, Google Drive) applied for different projects and teams collaborations.        
        \item Tutoring two students that developed a tool on Qt/C++ for DASH bandwidth estimation.        %Tutoring, during 6 months, of two students in a program entitled “Project S5” at Telecom Bretagne. They developed a linux tool on Qt/C++ for DASH bandwidth estimation.        
        \item Participation as volunteer on the organization of SBAC-PAD 2014 conference.
        \item Attended as participant at HTDC 2012, IMC 2013 (with student grant) and WOS3, and as speaker at COMPAS 2014, CNSM 2014 and ICPADS 2014.% WOS3 http://www.bretagne-networking.org/?page_id=1533
    \end{list3}
    \vspace{-1.5mm}%


    \textbf{Universidade Federal do Paraná}, Curitiba, Brazil.
    \hfill 2009 – 2011
    \\
    \textsl{M.Sc. in Information Technology.}
    \vspace{-3mm}\\\vspace{-1mm}%
    \begin{list3}
    \item Dissertation title: Connectivity Measures Based on Vertex Cuts Applied to Complex Networks (dissertation in Portuguese). Advisor: Dr. Elias P. Duarte Jr.
    \item Participation on evaluation experiments at secondary research topic entitled "An Efficient Strategy for Storing and Searching Binary Trees in WORM External Memory".
    \item Attended as participant to SBRC 2011 and as speaker at WTF 2011.
    %\item Attended to networks and distributed systems classes.
    \end{list3}
    \vspace{-1.5mm}%

    
    \textbf{Universidade Federal do Paraná}, Curitiba, Brazil.
    \hfill 2004 – 2007
    \\
    \textsl{B.Sc. in Computer Science.}
    \vspace{-3mm}\\\vspace{-1mm}%
    \begin{list3}
    %Uma Aplicação de Rádio Híbrida TCP/UDP e um Novo Protocolo para Streaming POTS
    \item Dissertation title: A Hybrid TCP/UDP Audio Application and a New Protocol for POTS Streaming (dissertation in Portuguese). Advisor: Dr. Elias P. Duarte Jr.
    \item Participated as a member of a research group with scholarship. 
    \item Volunteer alumnist at the yearly presentations for new students.
    \end{list3}
    \vspace{1.5mm}%
    \sectionline
    \vspace{-3mm}%
    
    
    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textcolor{resumecolor}{Professional\\Experience}}

    \textbf{No Zebra Network Ltd.}, Curitiba, Brazil.
    \hfill 2007 – 2011\\
    \textsl{Development Manager.}
    % \\
    %Following the model of start-ups, I had the chance to grow with the company, from only 5 employees to more than a hundred in five years.
    % Managed two teams (design and development), their projects and technical interviews.
    % Created and maintained websites that reached millions views per month with PHP, RoR and MySQL database. 
    % Produced HTML/CSS pages from PSD files for wide-range of browsers and devices with advanced dynamic scripts using JavaScript, AJAX and JS frameworks as JQuery and JqueryUI.
    % Deployed many optimizations for large scale web such as caching strategies, Varnish and Apache server configuration. 
    % Administrated Linux web servers with backups, monitoring tools with high availability requirements. 
    \vspace{-3mm}\\\vspace{-1mm}%
    \begin{list3}
    \item Managed two teams (design and development), their projects and technical interviews.
    \item Maintained and created large scale websites (millions views monthly) with PHP, RoR and MySQL. 
    \item Deployed many optimizations such as caching strategies, Varnish and Apache server configuration. 
    \item Administrated Linux servers with backups, monitoring tools with high availability requirements. 
    \end{list3}
    \vspace{-1.5mm}%

    \textbf{PET Computação UFPR}, Curitiba, Brazil.
    \hfill 2004 – 2006\\
    \textsl{Member of PET Computação UFPR with scholarship.}
    % \\
    %PET stands for Tutorial Education Program, is reserved to students with excellent grades inside Brazilian universities and is based on three main activities: research, teaching and science outreach.
    % Instructed PHP/MySQL classes to other graduation students, as well elaborated, along with another colleague, the book for this teaching. Responsible for the maintenance of the group website and creation of internal tools (library system and courses administration). Actively participated to local, regional and national meetings as representative of the group.
    \vspace{-3mm}\\\vspace{-1mm}%
    \begin{list3}
    \item Instructed PHP/MySQL classes and elaborated the book for this teaching.
    \item Maintained group website and created internal tools as library system and courses administration.
    \item Actively participated to local, regional and national meetings as group representative.
    \end{list3}
    \vspace{1.5mm}%
    \sectionline
    \vspace{-3mm}%

    %__________________________________________________________________________________________________________________
    % Technical Skills
    % \section{\mysidestyle Skills}
    % Python, R, Django, PHP, RoR, HTML/CSS, JS, C++, SQL, Git, Bash.

        %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textcolor{resumecolor}{Publications}}

    \small{
    \begin{list3}
        \item PIRES, K.; MONNET, S.; SENS, P. POPS: a popularity-aware live streaming service. ICPADS. 2014.
        \item PIRES, K.; SIMON, G. DASH in Twitch: Adaptive Bitrate Streaming in Live Game Streaming Platforms. VideoNext. 2014.
        \item MAILLÉ, P.; PIRES, K.; SIMON, G.; TUFFIN, B. How Neutral is a CDN? An Economic Approach. CNSM. 2014.
        \item LAURA, T.; APARICIO-PARDO, R.; PIRES, K.; SIMON, G.; BLANC, A.; FROSSARD, P. Optimal Selection of Adaptive Streaming Representations. TOMM. 2014.
        \item PIRES, K.; MONNET, S.; SENS, P. POPS : service de diffusion de flux vidéos live prenant en compte la popularité. COMPAS. 2014.
        \item PIRES, K.; SIMON, G. Book chapter entitled “Interactive Multimedia Applications on Clouds: Video services, games, others.” (to be published).
        \item DUARTE JR., E. P.; PIRES, K.; TAVARES, R. A. E. An Efficient Strategy for Storing and Searching Binary Trees in WORM External Memory. J. Information Science (JIS) 36(6):751-762. 2010.
        \item PIRES, K.; COHEN, J.; DUARTE JR., E. P. Medidas de Conectividade Baseadas em Cortes de Vértices Para Redes Complexas. XII WTF. 2011.
    \end{list3}
    }
    \vspace{1.5mm}%
    \sectionline
    \vspace{-3mm}%


    %__________________________________________________________________________________________________________________
    % Languages
    \section{\mysidestyle \textcolor{resumecolor}{Skills}}

    \textbf{Programming and Tools} Python (expert), R (expert), PHP (expert) JavaScript (expert), HTML/CSS (expert), C++(proficient), RoR (prior experience), Java (prior experience), C (prior experience); GIT, SVN, Apache, MySQL, SQLite, Linux.
    
    \vspace{-0.4cm}
    \textbf{Languages} English: fluent (speaking, reading, writing); French: intermediate (speaking, reading); basic (writing); Portuguese: native language.

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

